### 2025-04-21 evaluating-prediction-accuracy.qmd
20250421 - accuracy of weekly projections

```{r}

```

>>>>

```{r}
player_stats_weekly_subset <- player_stats_weekly %>% 
  filter(!is.na(player_id))

players_projectedPoints_weekly_combined$season <- as.integer(players_projectedPoints_weekly_combined$season)

player_stats_weekly_subset_IDs <- left_join(
  player_stats_weekly_subset,
  nfl_playerIDs_subset,
  by = c("player_id" = "gsis_id")
) %>% 
  filter(!is.na(mfl_id))

projectionsWithActuals_weekly <- full_join(
  player_stats_weekly_subset_IDs,
  players_projectedPoints_weekly_combined,
  by = c("mfl_id" = "id", "season", "week"),
  suffix = c("", "_proj"),
)

projectionsWithActuals_weekly <- projectionsWithActuals_weekly %>% 
  unite(
    "player_id_season_week",
    player_id,
    season,
    week,
    remove = FALSE
  )

playersWithHighProjectedOrActualPoints_weekly <- projectionsWithActuals_weekly %>% 
  filter(raw_points > 6 | fantasyPoints > 6) %>% 
  select(player_id_season_week) %>% 
  pull()

projectionsWithActuals_weekly_qb <- projectionsWithActuals_weekly %>% 
  filter(position_group == "QB")

projectionsWithActuals_weekly_rb <- projectionsWithActuals_weekly %>% 
  filter(position_group == "RB")

projectionsWithActuals_weekly_wr <- projectionsWithActuals_weekly %>% 
  filter(position_group == "WR")

projectionsWithActuals_weekly_te <- projectionsWithActuals_weekly %>% 
  filter(position_group == "TE")

projectionsWithActuals_weekly_k <- projectionsWithActuals_weekly %>% 
  filter(position == "K")

projectionsWithActuals_weekly_dl <- projectionsWithActuals_weekly %>% 
  filter(position_group == "DL")

projectionsWithActuals_weekly_lb <- projectionsWithActuals_weekly %>% 
  filter(position_group == "LB")

projectionsWithActuals_weekly_db <- projectionsWithActuals_weekly %>% 
  filter(position_group == "DB")
```

#### Overall {#sec-accuracyProjectionsWeeklyOverall}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly$raw_points,
  actual = projectionsWithActuals_weekly$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyOverall
#| fig-cap: "Calibration Plot for Weekly Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly$raw_points,
  y = projectionsWithActuals_weekly$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

#### Quarterbacks {#sec-accuracyProjectionsWeeklyQB}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_qb$raw_points,
  actual = projectionsWithActuals_weekly_qb$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyQBs
#| fig-cap: "Calibration Plot for Weekly Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly_qb$raw_points,
  y = projectionsWithActuals_weekly_qb$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly_qb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections of Quarterbacks"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_qb$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_qb$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

#### Running Backs {#sec-accuracyProjectionsWeeklyRB}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_rb$raw_points,
  actual = projectionsWithActuals_weekly_rb$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyRBs
#| fig-cap: "Calibration Plot for Weekly Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly_rb$raw_points,
  y = projectionsWithActuals_weekly_rb$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly_rb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections of Running Backs"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_rb$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_rb$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

#### Wide Receivers {#sec-accuracyProjectionsWeeklyWR}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_wr$raw_points,
  actual = projectionsWithActuals_weekly_wr$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyWRs
#| fig-cap: "Calibration Plot for Weekly Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly_wr$raw_points,
  y = projectionsWithActuals_weekly_wr$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly_wr,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections of Wide Receivers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_wr$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_wr$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

#### Tight Ends {#sec-accuracyProjectionsWeeklyTE}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_te$raw_points,
  actual = projectionsWithActuals_weekly_te$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyTEs
#| fig-cap: "Calibration Plot for Weekly Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly_te$raw_points,
  y = projectionsWithActuals_weekly_te$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly_te,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections of Tight Ends"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_te$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_te$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

#### Kickers {#sec-accuracyProjectionsWeeklyK}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_k$raw_points,
  actual = projectionsWithActuals_weekly_k$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyKs
#| fig-cap: "Calibration Plot for Weekly Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly_k$raw_points,
  y = projectionsWithActuals_weekly_k$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly_k,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections of Kickers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_k$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_k$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

#### Defensive Linemen {#sec-accuracyProjectionsWeeklyDL}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_dl$raw_points,
  actual = projectionsWithActuals_weekly_dl$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyDLs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly_dl$raw_points,
  y = projectionsWithActuals_weekly_dl$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly_dl,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections of Defensive Linemen"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_dl$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_dl$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

#### Linebackers {#sec-accuracyProjectionsWeeklyLB}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_lb$raw_points,
  actual = projectionsWithActuals_weekly_lb$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyLBs
#| fig-cap: "Calibration Plot for Weekly Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly_lb$raw_points,
  y = projectionsWithActuals_weekly_lb$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly_lb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections of Linebackers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_lb$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_lb$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```

#### Defensive Backs {#sec-accuracyProjectionsWeeklyDB}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_db$raw_points,
  actual = projectionsWithActuals_weekly_db$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotWeeklyDBs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_weekly_db$raw_points,
  y = projectionsWithActuals_weekly_db$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

ggplot2::ggplot(
  data = projectionsWithActuals_weekly_db,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(plotRangeMin, plotRangeMax),
    expand = FALSE) +
  scale_x_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  scale_y_continuous(breaks = seq(0, plotRangeMax, by = 5)) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "gam",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of GAM model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Weekly Projections of Defensive Backs"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_db$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_db$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)
```
